---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  color: "#2D242C";
  background-color:#6F8695;
  font-family: Arial;
}

h1 {
  color: #443742;
  background-color: #F8B5BF;
  padding: 20px;
}

h2 {
  color: #2D242C;
  background-color: #FAC6CE;
  padding: 15px;
}

h3 {
  color: #2D242C;
  background-color: #F8B5BF;
  padding: 10px;
}
a {
 color: #000000;
}
```

## Communication in the Digital Age 
### How many notifications is too many?

Have you ever felt stress or anxiety from the sheer number of notifications you receive in a day? In the modern world where we are always reachable, it can be overwhelming getting messages all day long, from so many different apps, for so many different reasons. The intent of this report is to show which apps had the most notifications, and what the main purpose of those notifications was, and also whether or not they required a response. This is helpful data to look at if you are wanting to minimise stress from your phone, and mute certain notifications, or set up a system in which you reply to certain notifications at different times to minimise stress.

This data is analysing the notifications I received over a few days on my phone. The data includes which apps the notifications were from, the main purpose of the notification, and how many notifications from the same app or person were received within 5 minutes of the first notification.

### How Many Notifications?

```{r}

library(tidyverse)

#reading in CSV file and rename the variables of the data frame

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSoLnnQbeTDg3aNisdQvee9_54Ic0Xz0Wr5Js2j07ljE1Ef1zqnMMu2UrGXEckAPnBnD315yH4exXKK/pub?output=csv")%>%
  rename(app = 2,
         purpose = 3,
         time = 4,
         notif_num = 5,
         response = 6)


#creating vectors
app_vector <- logged_data$app
purpose_vector <- logged_data$purpose
time_vector <- logged_data$time
notif_num_vector <- logged_data$notif_num
response_vector <- logged_data$response


paste("The highest number of notifications received from the same person or app in 5 minutes was", max(notif_num_vector))

#getting the mean of notif_num
mean_notif <- logged_data%>%
                select(notif_num)%>%
                sum()/length(notif_num_vector)
rounded_mean_notif <- round(mean_notif,0)

paste("The mean number of notifications received from the same person or app in 5 minutes was", rounded_mean_notif)

#plot of how many notifications where received in a five minute span
logged_data%>%
  ggplot() +
  geom_bar(aes(x = notif_num),
               fill = "#B5A6B2") +
    labs(title = "Notifications Received Within Five Minutes Of The First Notification",
         y = "Count",
         x = "Number of Notifications"
     )
```

### What Is The Point Of A Notification?

This plot shows the main purpose of each notification that is received.

```{r}
#plot showing the purpose of the notifications
#separate the data that has more than one value
logged_data_longer <- logged_data %>%
  separate_rows(purpose, sep = ", ")
#then put that data into ggplot
logged_data_longer  %>%
  ggplot() +
  geom_bar(aes(x = purpose),
           fill = "#7E8D68") +
    labs(title = "How Many Notifications Were Received for Different Purposes?",
         y = "Count",
         x = "Purpose of the Notification"
         )

```

### Why Do I Need So Many Apps?

This plot shows the purpose of the notification, and which app it came from, to show which apps are more work focused, which are more school focused, and which are just for fun.

```{r}
#graph for what app the notification was from versus what the notification was for
logged_data_longer %>%
  ggplot() +
  geom_bar(aes(x = app, fill = purpose)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.4, hjust=0.5)) +
  scale_fill_manual(values = alpha(c("#B5A6B2", "#7E8D68","#778C96", "#EDD9A3"), 1)) +
  labs(title = "Purpose vs App",
       subtitle = "Comparing which apps had notifications for which purpose",
       caption = "Source: Google Forms",
       y = "Number of Notifications",
       x = "App")


```

### I'll Just Reply Later!

This plot shoes which notifications from which apps needed to be replied to.

```{r}
#graph of notifications needing responses versus the apps the notifications were received from
logged_data %>%
  ggplot() +
  geom_bar(aes(x = app, fill = response)) +
  scale_fill_manual(values = alpha(c("#B5A6B2", "#778C96"), 1)) +
  labs(title = "What Apps Need Responses for Notifications",
       subtitle = "Comparing whether a response is required by what app the notification was received on",
       caption = "Source: Google Forms",
       y = "Number of Notifications",
       x = "App")
```
